---
title: "Analysis of historical daily returns from the DJIA"
author: "J. R. Minter"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    css: theme/custom.css
---
```{r pre_load_lib, echo=FALSE}
# pre-load libraries
library(knitr)
library(png)
library(grid)
```

## Introduction

The purpose of this project is to analyse the historical daily
returns from the Dow Jones Industrial Average (DJIA).

## Data Source

Historical data was obtained from
[measuringworth.com](http://measuringworth.com/DJA/) and 
downloaded as a `.csv` file. The original file was stored in 
this repository without modification.
They describe their data cleaning process
[here](http://measuringworth.com/DJA/DowSource.htm).

The data analyzed here was downloaded on `2015-08-14`.

**Note:** This is a work in progress and is *not* ready for prime time.

## Exploratory Data Analysis

A scatterplot of the daily returns is shown below

```{r dr_scatter_plot, fig.width=6.5,echo=FALSE}
img <- readPNG("./knitr/inc/png/dji-daily-ret.png")
 grid.raster(img)
```

A histogram is plotted below


```{r dr_histo_plot, fig.width=7,echo=FALSE}
img <- readPNG("./knitr/inc/png/dji-daily-ret-histo.png")
 grid.raster(img)
```

Now let's look at the tails

```{r dr_histo_tails_plot, fig.width=7,echo=FALSE}
img <- readPNG("./knitr/inc/png/dji-daily-ret-histo-lo.png")
 grid.raster(img)
```

And at a qq plot

```{r dr_qq_plot, fig.width=7,echo=FALSE}
img <- readPNG("./knitr/inc/png/dji-daily-ret-qq.png")
 grid.raster(img)
```


```{r cc_by, fig.width=1,echo=FALSE}
img <- readPNG("./knitr/inc/png/cc-by.png")
 grid.raster(img)
```
